The Astropy Project: \\ Sustaining and Growing a Community-oriented Open-source Project and the Latest Major Release (v5.0) of the Core Package

### 2022-02-10 src/ms.tex
Remove pytest from whatsnew list
Expand on future plans of uncertainties

\begin{itemize}
%  \item Time Series sub-package (V3.1: New Box Least Squares Periodogram)
%  \item Uncertainties and Distributions
  \item ERFA module is now it’s own thing; Obliquely tie in that units
    remains in astropy
  \item ? Pytest plugin ecosystem
%  \item A new SpectralCoord class for representing and transforming spectral quantities
%    Velocity in Coordinates
%  \item WCS API : A shared Python interface for World Coordinate Systems
%        Include APE 14 reference
\end{itemize}

@@

>>>>

\begin{itemize}
%  \item Time Series sub-package (V3.1: New Box Least Squares Periodogram)
%  \item Uncertainties and Distributions
  \item ERFA module is now it’s own thing; Obliquely tie in that units
    remains in astropy
%  \item ? Pytest plugin ecosystem -> done elsewhere
%  \item A new SpectralCoord class for representing and transforming spectral quantities
%    Velocity in Coordinates
%  \item WCS API : A shared Python interface for World Coordinate Systems
%        Include APE 14 reference
\end{itemize}

@@

Apart from Monte-Carlo error propagation, the plan for
\astropysubpkg{uncertainties} is to also support the case where values
have associated uncertainties, and these are propagated assuming that
they are normally distributed, but tracking covariances.  One
implementation problem to be solved is when to {\em stop} tracking
covariances.  For instance, a simple operation such as subtracting the
mean from $N$ data points implies that all data points are now
covariant with each other, i.e., one has to carry $N\times N$
covariances.  For a large image, that becomes not just pointless but
also prohibitive in terms of memory and CPU usage.
